Hydras \& Co.

### 2023-06-22 doc/chapter-fol.tex
small changes in documentation

\inputsnippets{FolExamples/substExample1}

Thus, the function (\texttt{fun f => substF L f i t}) doesn't commute with all \texttt{Formula}'s constructors.

\inputsnippets{FolExamples/substExample2}

From this little example, we can guess that the function
\texttt{substF} which is assumed to compute the substitution in a formula $F$ the substitution of a term $t$ to the free occurrences of a variable $v$ will not be implemented as a direct structural recursive function. For instance, the formula $G$, obtained through a variable renaming, is not a strict subterm of $F$.

Thus, we cannot expect do define simply this operation by 
structural recursion over formulas. 
In~\cite{Goedel}, the approach is to define a \emph{measure}
which maps every formula to a natural number, then define substitution in such a way that the substitution of a term to a free variable in a strict sub-formula  of a formula $F$ is smaller
(w.r.t. this measure) than $F$. 
Then substitution could be defined by well-founded recursion.

Fortunately, such a measure : the \emph{depth} of a formula,
can be easily defined by structural recursion.

@@

The function \texttt{depth} computes the \emph{depth} of the 
 skeleton of any formula, and allows us to define a well-founded strict order on 
\texttt{Formula $L$}.

@@

@@

The library~\href{../theories/html/hydras.Ackermann.fol.html}{Ackermann.fol} contains several induction principles, applied 
throughout \texttt{Ackermann} and \texttt{Goedel} projects.

>>>>

%\inputsnippets{FolExamples/substExample1}

% Thus, the function (\texttt{fun f => substF L f i t}) doesn't commute with all \texttt{Formula}'s constructors.

% \inputsnippets{FolExamples/substExample2}

% From this little example, we can guess that the function
% \texttt{substF} which is assumed to compute the substitution in a formula $F$ the substitution of a term $t$ to the free occurrences of a variable $v$ will not be implemented as a direct structural recursive function. For instance, the formula $G$, obtained through a variable renaming, is not a strict subterm of $F$.

% Thus, we cannot expect do define simply this operation by 
% structural recursion over formulas. 
% In~\cite{Goedel}, the approach is to define a \emph{measure}
% which maps every formula to a natural number, then define substitution in such a way that the substitution of a term to a free variable in a strict sub-formula  of a formula $F$ is smaller
% (w.r.t. this measure) than $F$. 
% Then substitution could be defined by well-founded recursion.

Fortunately, \coq allows us to define functions by well-founded recursion, and in particular with the help of a \emph{measure} mapping every formula to an already known well-founded type.

@@

The function \texttt{depth} computes the \emph{depth} of  any formula, \emph{i.e} the height of the sub-tree made
by erasing all nodes but those nodes labelled with
\texttt{allH}, \texttt{impH} and \texttt{notH}.

@@

Lemma \texttt{fol.Formula\_depth\_rec} is the basic
induction principle based on depth.

\inputsnippets{FolExamples/depthRec}

@@

The library~\href{../theories/html/hydras.Ackermann.fol.html}{Ackermann.fol} contains several derived induction principles, applied 
throughout \texttt{Ackermann} and \texttt{Goedel} projects.
